ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-18 pyked.tex
clarified current version

This section will provide a brief introduction to the \ck{} database format.
This is not a complete listing of available fields and more complete examples of
\ck{} files can be found in the \pybox|tests| directory of the \pk{} package. In
addition, in Section~\ref{sec:usage-example}, we will provide examples of \ck{}
files. We indicate \yabox|yaml| keywords or values using text with gray background,
and \pybox|Python| code using text with a yellow background.

\ck{} files use the YAML data serialization format~\autocite{yaml:1.2}. This
format offers the advantages of being human readable, written in plain text, and
having parsers in most common programming languages, including Python, C++, Java,
Perl, MATLAB, and many others. The YAML syntax is quite simple. The basic file
structure is made of mappings, delimited by a colon. The key for the mapping is
on the left of the colon, and the value on the right can be a single value,
a sequence of values, a nested mapping, or some combination of these:
%
\begin{yamlbox}
key1: value  # Single-value mapping
key2:  # Sequence format
  - value
  - value
key3:  # Nested mapping
  key4: 0
key5:  # Sequence of mappings
  - key-s1: 0
    key-s2: value
  - key-s2: value
    key-s1: 0
\end{yamlbox}

>>>>

This section will provide a brief introduction to the current version of the
\ck{} database format, v0.1.6, which represents a functional standard
for documenting autoignition measurements in shock tubes and rapid compression machines.
This is not a complete listing of available fields and more complete examples of
\ck{} files can be found in the \pybox|tests| directory of the \pk{} package. In
addition, in Section~\ref{sec:usage-example}, we will provide examples of \ck{}
files. We indicate \yabox|yaml| keywords or values using text with gray background,
and \pybox|Python| code using text with a yellow background.

\ck{} files use the YAML data serialization format~\autocite{yaml:1.2}. This
format offers the advantages of being human readable, written in plain text, and
having parsers in most common programming languages, including Python, C++, Java,
Perl, MATLAB, and many others. The YAML syntax is quite simple: the basic file
structure is made of mappings, delimited by a colon. The key for the mapping is
on the left of the colon, and the value on the right can be a single value,
a sequence of values, a nested mapping, or some combination of these:
%
\begin{yamlbox}
key1: value  # Single-value mapping
key2:  # Sequence format
  - value
  - value
key3:  # Nested mapping
  key4: 0
key5:  # Sequence of mappings
  - key-s1: 0
    key-s2: value
  - key-s2: value
    key-s1: 0
\end{yamlbox}
